%-----------------------------------------------------------------------------------------------------------------------------------------------%
%	The MIT License (MIT)
%
%	Copyright (c) 2021 Jitin Nair
%
%	Permission is hereby granted, free of charge, to any person obtaining a copy
%	of this software and associated documentation files (the "Software"), to deal
%	in the Software without restriction, including without limitation the rights
%	to use, copy, modify, merge, publish, distribute, sublicense, and/or sell
%	copies of the Software, and to permit persons to whom the Software is
%	furnished to do so, subject to the following conditions:
%
%	THE SOFTWARE IS PROVIDED "AS IS", WITHOUT WARRANTY OF ANY KIND, EXPRESS OR
%	IMPLIED, INCLUDING BUT NOT LIMITED TO THE WARRANTIES OF MERCHANTABILITY,
%	FITNESS FOR A PARTICULAR PURPOSE AND NONINFRINGEMENT. IN NO EVENT SHALL THE
%	AUTHORS OR COPYRIGHT HOLDERS BE LIABLE FOR ANY CLAIM, DAMAGES OR OTHER
%	LIABILITY, WHETHER IN AN ACTION OF CONTRACT, TORT OR OTHERWISE, ARISING FROM,
%	OUT OF OR IN CONNECTION WITH THE SOFTWARE OR THE USE OR OTHER DEALINGS IN
%	THE SOFTWARE.
%
%
%-----------------------------------------------------------------------------------------------------------------------------------------------%

%----------------------------------------------------------------------------------------
%	DOCUMENT DEFINITION
%----------------------------------------------------------------------------------------

% article class because we want to fully customize the page and not use a cv template
\documentclass[a4paper,10pt]{article}

%----------------------------------------------------------------------------------------
%	FONT
%----------------------------------------------------------------------------------------

% % fontspec allows you to use TTF/OTF fonts directly
% \usepackage{fontspec}
% \defaultfontfeatures{Ligatures=TeX}

% % modified for ShareLaTeX use
% \setmainfont[
% SmallCapsFont = Fontin-SmallCaps.otf,
% BoldFont = Fontin-Bold.otf,
% ItalicFont = Fontin-Italic.otf
% ]
% {Fontin.otf}

%----------------------------------------------------------------------------------------
%	PACKAGES
%----------------------------------------------------------------------------------------
\usepackage{url}
\usepackage{parskip}

%other packages for formatting
\RequirePackage{color}
\RequirePackage{graphicx}
\usepackage[usenames,dvipsnames]{xcolor}
\usepackage[scale=0.9]{geometry}

%tabularx environment
\usepackage{tabularx}

%for lists within experience section
\usepackage{enumitem}

% centered version of 'X' col. type
\newcolumntype{C}{>{\centering\arraybackslash}X}

%to prevent spillover of tabular into next pages
\usepackage{supertabular}
\usepackage{tabularx}
\newlength{\fullcollw}
\setlength{\fullcollw}{0.47\textwidth}

%custom \section
\usepackage{titlesec}
\usepackage{multicol}
\usepackage{multirow}

%CV Sections inspired by:
%http://stefano.italians.nl/archives/26
\titleformat{\section}{\Large\scshape\raggedright}{}{0em}{}[\titlerule]
\titlespacing{\section}{0pt}{10pt}{10pt}

%for publications
\usepackage[style=authoryear,sorting=ynt, maxbibnames=2]{biblatex}

%Setup hyperref package, and colours for links
\usepackage[unicode, draft=false]{hyperref}
\definecolor{linkcolour}{rgb}{0,0.2,0.6}
\hypersetup{colorlinks,breaklinks,urlcolor=linkcolour,linkcolor=linkcolour}
\addbibresource{citations.bib}
\setlength\bibitemsep{1em}

%for social icons
\usepackage{fontawesome5}

%debug page outer frames
%\usepackage{showframe}


% job listing environments
\newenvironment{jobshort}[2]
    {
    \begin{tabularx}{\linewidth}{@{}l X r@{}}
    \textbf{#1} & \hfill &  #2 \\[3.75pt]
    \end{tabularx}
    }
    {
    }

\newenvironment{joblong}[2]
    {
    \begin{tabularx}{\linewidth}{@{}l X r@{}}
    \textbf{#1} & \hfill &  #2 \\[3.75pt]
    \end{tabularx}
    \begin{minipage}[t]{\linewidth}
    \begin{itemize}[nosep,after=\strut, leftmargin=1em, itemsep=3pt,label=--]
    }
    {
    \end{itemize}
    \end{minipage}
    }



%----------------------------------------------------------------------------------------
%	BEGIN DOCUMENT
%----------------------------------------------------------------------------------------
\begin{document}

% non-numbered pages
\pagestyle{empty}

%----------------------------------------------------------------------------------------
%	TITLE
%----------------------------------------------------------------------------------------

% \begin{tabularx}{\linewidth}{ @{}X X@{} }
% \huge{Your Name}\vspace{2pt} & \hfill \emoji{incoming-envelope} email@email.com \\
% \raisebox{-0.05\height}\faGithub\ username \ | \
% \raisebox{-0.00\height}\faLinkedin\ username \ | \ \raisebox{-0.05\height}\faGlobe \ mysite.com  & \hfill \emoji{calling} number
% \end{tabularx}

\begin{tabularx}{\linewidth}{@{} C @{}}
\Huge{KIERAN KLUKAS} \\[7.5pt]
Columbus, Ohio \textbar{} +1 380 (254) 2562 \textbar{} me@dunkirk.sh \textbar{} www.linkedin.com/in/kieran-klukas
\end{tabularx}

%----------------------------------------------------------------------------------------
%	EDUCATION
%----------------------------------------------------------------------------------------
\section{EDUCATION}

\textbf{Cedarville University} \hfill Cedarville, OH\\
Dual Enrollment, Computer Engineering \hfill Anticipated 05/2025\\
Completing all senior year courses through Cedarville's Dual Enrollment program and on track to finish freshman Computer Engineering requirements before graduating high school.

%----------------------------------------------------------------------------------------
% EXPERIENCE SECTIONS
%----------------------------------------------------------------------------------------

\section{SUMMARY}
17-year-old homeschooled high school student with strong technical and interpersonal skills seeking to obtain an internship in software engineering or cybersecurity. Passionate about hardware and software integration, robotics, and cybersecurity. Goals include gaining real-world experience and working in the technology industry. Additional skills include:
\begin{itemize}[nosep,leftmargin=1em, itemsep=3pt,label=$\bullet$]
\item 5+ years Programming Experience
\item KiCAD \& Hardware Design
\item Server Management \& Linux
\end{itemize}

\section{EXPERIENCE}

\textbf{Cedarville University Center for Advancement of Cybersecurity} \hfill Cedarville, OH\\
\textit{GenCyber Camp Participant} \hfill 06/2025
\begin{itemize}[nosep,after=\strut, leftmargin=1em, itemsep=3pt,label=--]
\item Achieved 2nd place in Cyber Skyline Cyber Lab Kit Intro CTF with 1st place finishing time of 57:58.
\item Received Cedarville University Center for Advancement of Cybersecurity challenge coin.
\end{itemize}

\textit{Crimson Defense CDCTF Team Member - Prochoroume} \hfill 2025
\begin{itemize}[nosep,after=\strut, leftmargin=1em, itemsep=3pt,label=--]
\item Placed 6th out of 51 college teams in cybersecurity capture the flag competition.
\item Specialized in social engineering and reverse engineering challenges.
\end{itemize}

\textbf{Elmer W. Engstrom School of Engineering and Computer Science} \hfill Cedarville, OH\\
\textit{Cardboard Canoe Race Team Member} \hfill 2025
\begin{itemize}[nosep,after=\strut, leftmargin=1em, itemsep=3pt,label=--]
\item Worked with a 4-person team to design and build a canoe with a 40' roll of cardboard and a roll of packing tape.
\item Placed 2nd overall in the race portion of the project.
\end{itemize}

\textbf{FIRST} \hfill Columbus, OH\\
\textit{Chair of the Outreach and Sustainability Committee for the Ohio Youth Advisory Council} \hfill 08/2025--Present
\begin{itemize}[nosep,after=\strut, leftmargin=1em, itemsep=3pt,label=--]
\item Lead team leadership and public outreach initiatives for Ohio FIRST programs.
\item Coordinate sustainability efforts across multiple robotics teams statewide.
\end{itemize}

\textit{Programming Team Co-lead @ FRC team 1317} \hfill 11/2023--Present
\begin{itemize}[nosep,after=\strut, leftmargin=1em, itemsep=3pt,label=--]
\item Co-lead programming team for competitive robotics using WPILib framework.
\item Develop and maintain robot control systems for FIRST Robotics Competition.
\end{itemize}

\textbf{Hack Club} \hfill Remote\\
\textit{Volunteer Software Developer} \hfill 10/2023--Present
\begin{itemize}[nosep,after=\strut, leftmargin=1em, itemsep=3pt,label=--]
\item Designed and built hackatime scaling it to handle over 25,000 simultaneous teenagers logging coding time during High Seas event.
\item Developed multiple Slack bots to moderate and facilitate events through the Hack Club Slack workspace.
\item Utilized PostgreSQL and server management skills to ensure system reliability.
\end{itemize}

%----------------------------------------------------------------------------------------
%	ACTIVITIES
%----------------------------------------------------------------------------------------
\section{ACTIVITIES}
\begin{center}
{\small Cybersecurity CTF Competitions -- 2024--Present \textbar{} FIRST Robotics Competition -- 2023--Present \textbar{} Hack Club Community Volunteer -- 2023--Present \textbar{} Church Audio/Visual Ministry -- 2023--Present \textbar{} Orchestra -- 2022--2024}
\end{center}

\vfill
\center{\footnotesize Last updated: \today}

\end{document}
